Structural controllability of ecological networks

### 2018-06-22 paper/manuscript.Rmd
Add histogram of control capacity and move superior model plots to supp

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*1.5, fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines indicate the median values of each distribution."}
drake::loadd(fig_emp_controllability)

cowplot::plot_grid(plotlist = fig_emp_controllability, 
                   ncol = 1, 
                   align = "v")
```

@@

```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Relationship between the most important variables in the models of control capacity (a, b) and the probability of being a superior species (c, d). The plots show the values predicted by most parsimonious model for each response variable. The model for control capacity include a random effect for the trophic guild , while the model of superior probability does not include any random effect that distinguish between plants and pollinators. The invasive species are depicted with solid orange circles."}
drake::loadd(fig_control_capacity)
library(ggplot2)
fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
fig_control_capacity[[4]] <- fig_control_capacity[[4]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

>>>>

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*1.5, fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) Relationship between the asymmetry plant/pollinator richness and $n_D$. The plot shows the values predicted by the most parsimoniouls model. (c) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines indicate the median values of each distribution."}
drake::loadd(fig_emp_controllability)
cowplot::plot_grid(plotlist = fig_emp_controllability, 
                   ncol = 1, 
                   align = "v")
```

```{r}
drake::loadd(sl_characteristics)
crit <- sl_characteristics %>% 
  filter_networks_df(metadata) %>%
  dplyr::group_by(net_name) %>%
  dplyr::summarise(n_crit = sum(control_capacity == 1), 
                   n_sp = n()) %>%
  dplyr::mutate(p_crit = n_crit/n_sp)

pcrit_ran <- range(crit$p_crit)
ncrit_ran <- range(crit$n_crit)
pcrit_med <- median(crit$p_crit)
```

@@

```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Density plot of the control capacity $\\phi$ of (a) plants and (b) pollinators. (c, d) Relationship between the most important variables in the models of control capacity. The plots show the values predicted by most parsimonious model for each response variable. The model included a random effect for the trophic guild and hence trends of plants and pollinators are shown separately. The invasive species are depicted with solid orange circles."}
drake::loadd(fig_control_capacity)
library(ggplot2)
fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
fig_control_capacity[[4]] <- fig_control_capacity[[4]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

### 2018-06-22 paper/supp-info.Rmd
Add histogram of control capacity and move superior model plots to supp

>>>>

```{r fig-superior, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between the most important variables in the models of superior probability. The plots show the values predicted by most parsimonious model. Invasive species are depicted with solid orange circles."}
drake::loadd(fig_superior)
cowplot::plot_grid(plotlist = fig_superior, ncol = 2)
```
